\textbf{SYNOPSIS}

### 2017-01-26 synopsis.tex
final changes

Our work in this chapter is centred on testing the performance of the several algorithms proposed in earlier chapters along with the existing algorithms. For the empirical evaluations, we use the two loss functions. The first one is quadratic  loss  function and the other is Fourth-order loss function. We perform experiments for both the noisy and noise-less settings. We use normalized loss and normalized MSE (NMSE) as performance metrics for evaluating the algorithms. NMSE is the ratio $\l \theta_{n_\text{end}} - \theta^* \r^2 / \l \theta_0 - \theta^*\r^2$, while normalized loss is the ratio $f(\theta_{n_\text{end}})/f(\theta_0)$. Here $n_\text{end}$ denotes the iteration number when the algorithm stopped updating its parameter. From the results, we make the following observations:

>>>>

Our work in this chapter is centred on testing the performance of the algorithms we proposed in the earlier chapters along with the existing algorithms in the literature. For the empirical evaluations, we use two loss functions. The first one is quadratic  loss  function and the other is a fourth-order loss function. We perform experiments for both the noisy and noise-less settings. We use normalized loss and normalized mean squared error (NMSE) as performance metrics for evaluating the algorithms. NMSE is the ratio $\l \theta_{n_\text{end}} - \theta^* \r^2 / \l \theta_0 - \theta^*\r^2$, while normalized loss is the ratio $f(\theta_{n_\text{end}})/f(\theta_0)$. Here $n_\text{end}$ denotes the iteration number when the algorithm stop updating its parameter. From the results, we make the following observations:
